---
title: "todor-notes"
author: "Bryan Jenks"
date: "8/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(todor)
```

```{r the_plain_function}
# What the function actually does ----

# TODO here is a comment follow up note
todor::todor()
```

```{r single_file_call}
# HINT: By default todor works on projects, but you can call todor_package to search an entire package.

# Call todor on a single file only, default is project ----
# ....Files could work with the here() package ----
todor::todor_file("notes.Rmd")
```

```{r pkg_calls}
# Calling todor on a whole package ----
todor::todor_package()
```

```{r addin_func_calls}
# Addins menu options ----
# ....can call on a single file ----
todor::todor_file_addin()
# ....Can call on a whole package ----
todor::todor_package_addin()
# ....Or a whole project with a .Rproj file ----
todor::todor_project_addin()
```

```{r specific_types}
# Look for specific types ----
# FIXME this is a fixit comment, refactor this item!!!1
todor::todor(c("TODO", "FIXME"))
# Types it can detect by default ----
## FIXME, TODO, CHANGED, IDEA, HACK, NOTE, REVIEW, BUG, QUESTION, COMBAK, TEMP.
# ....how to change searchable types for the function ----
options(todor_patterns = c("FIXME", "TODO", "BRYAN"))

# BRYAN this is not in all caps
```

# Markdown Comments

<!-- BUG Change this section. -->

**Very important element.**

# Controlling TODOR Behavior

`todor_rmd` - when set to TRUE it searches also through Rmd files (default TRUE).

`todor_rnw` - when set to TRUE it searches also through Rnw files (default FALSE).

`todor_rhtml` - when set to TRUE it searches also through Rhtml files (default FALSE).

`todor_exlude_packrat` - when set to FALSE, all files in the "packrat" directory are excluded (default TRUE).

`todor_exclude_r` - when TRUE, it ignores R and r files (default FALSE)


```{r search_opts}
# This is to expand the scope of searches ----
# ....how to switch off markdown search ----
options(todor_rmd = T) # default is on  / TRUE
# ....how to switch off rnw search ----
options(todor_rnw = T) # sweave files
# ....how to switch off rhtml search ----
options(todor_rhtml = T) # R Notebooks
# ....how to switch off packrat search ----
options(todor_exclude_packrat = T) # ignore all notes in files downloaded by packrat you probably very much want this
# ....how to switch off r/R search ----
options(todor_exclude_r = F) # rscript files you probably dont want to ignore these default is FALSE
```






